\texttt{vqtl}: An \texttt{R} package for Mean-Variance QTL Mapping

### 2018-06-07 Package_vqt_Manuscript.tex
edits

Based on these benchmarks, it is clear that the workflow presented here is practical for QTL mapping F2 intercross and similar populations on modern, multi-core scientific computers.
Populations with many recombinations, where dense genotyping arrays that interrogate $\textgreater$ 10,000 loci are relevant, could not be practically analyzed with package \texttt{vqtl} in this way.
However, both statistical and computational steps could be taken to make such a study feasible.
Statistically, techniques could be used that allow for large-scale analysis without permutation testing \citep{Efron2004}.
Computationally, the software could be changed to run on a computer cluster, rather than on a single computer \citep{Jette2003a,Marchand2017}.

>>>>

Based on these benchmarks, it is clear that the workflow presented here is practical for QTL mapping F2 intercross and similar populations on modern, multi-core scientific computers.
Populations with many recombinations, where dense genotyping arrays that interrogate $\textgreater$ 10,000 loci are relevant, could not be practically analyzed with package \texttt{vqtl} in this way.
\RC
{
    \WV
    {
        However, both statistical and computational steps could be taken to make such a study feasible.
    }{
        Are there ways to make efficient the analysis of multiple traits on the same population? For example, in the standard analysis of gene expression data, rint-ing a probe then performing permutations on it provides thresholds that will be valid for all other rint-ed probes (assuming no missingness; eg, ask Greg). Not sure if this applies in our situation... needs more thought.
    }
}
{
    I think simply suggesting that larger-scale analysis might be possible is appropriate here, since we haven't done it and haven't even worked out how to do it.
    I don't think it makes sense for us to try to figure out how we would have done a different study and report exactly how we would have done that.
}
Statistically, techniques could be used that allow for large-scale analysis without permutation testing \citep{Efron2004}.
Computationally, the software could be changed to run on a computer cluster, rather than on a single computer \citep{Jette2003a,Marchand2017}.
\RC
{
    \WV{}
    {Does this section extend the paper beyond the required limits.}
}
{
    Yes.  Do you think they will notice/care?
}
